Variational Monte Carlo on bosonic systems

### 2018-01-25 project_1/article/article.tex
Add the gradient and Laplacian of the SPF

>>>>

            To go from here we have to find the gradient and the Laplacian of
            the single particle functions, $\phi(\vf{r}_k)$, and the interaction
            functions $u(r_{km})$. For the single particle functions we use
            Cartesian coordinates when finding the derivatives whereas we for
            the interaction functions will use spherical coordinates and do a
            variable substitution. Beginning with the gradient of the single
            particle functions we get
                \nabla_k\exp\bigl[
                    -\alpha(x_k^2 + y_k^2 + \beta z_k^2)
                -2\alpha
                (x_k\vf{e}_i + y_k\vf{e}_j + \beta z_k\vf{e}_k)
                \phi(\vf{r}_k),
            note that the subscripts on the unit vectors $\vf{e}_i$ are
            \textit{not} the same as the subscripts used for its components. The
            Laplacian yields
                \nabla_k^2\phi(\vf{r}_k)
                -2\alpha
                \big(
                    2 + \beta
                \bigr)
                \phi(\vf{r}_k)
                \nonumber \\
                + 4\alpha^2
                \bigl(
                    x_k^2 + y_k^2 + \beta^2z_k^2
                \bigr)
                \phi(\vf{r}_k).
